---
title: "CodeBook"
author: "Mike Anderson"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## UCI HAR Dataset Cleaning and Prcessing

Data: These data were collected from 30 participants wearing galaxy s mobile phone while performing 6 activities.  Measures of accelaration and gyroscope position were recorded, processed and normalized prior to this cleaning and prcessing.  For more information on these data please see <http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones>.

### Original data structure.
Data was stored on multiple .txt files within a zip folder at  https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip.  30\% of the data had been randomly selected for a hold out test data ("_test") set while the remaining data was used to develop models ("_train").  The data can be dowloaded to a created file named "data" and the .txt files listed using the following code.


### Data Extraction
We next extact data to the local folder can be done using this code and the working directory set to read in from the extacted "CDI HAR Dataset folder"



### Read Data
We now read the .txt file data and name the columns of each data set.The Inertial Signals data provide 128 elements that are unamed/described from the UCI source so these data are not considered in this codebook


### Processing Data Steps
Here we combine the subject identifiers, the activies performed and the outcome measures into 1. a single file for each test and training data set and 2. in to a single combined file the merges the test and training data sets with the subject and activity identifiers.  We also investigate the stucture of each variable and each varaible name in preparation for precessing


### Removing varibles
Here we keep only the variables with subject ids, the activity labels, and variables with the terms Mean or Standard Deviation as indicated by 'mean' or 'std' in the name.


###Variable Renaming
Variable structure will remain the same but varaible names will be modified to be more informative.  We also subsitute the activity lable numbers with the more descriptive lables. Finally we relabel the variables to be more informative of it they are a "Time" or "Frequency" veraible from the "Accelrometer" or "Gyroscope measure"


### Create additional data set 
This data set consists of the means of each variable by subject and activity.


### Final Code Books
A code book of each of the final data sets and renamed varialbes can be obtained using the code below.

#### Final data set

```{r,eval=F}
#have a look at the structs of each created data set 
str(comb.mean.std)

'data.frame':	10299 obs. of  81 variables:
 $ subject                                                      : int  2 2 2 2 2 2 2 2 2 2 ...
 $ Activity                                                     : chr  "STANDING" "STANDING" "STANDING" "STANDING" ...
 $ Time Body Acceleration Mean X                                : num  0.257 0.286 0.275 0.27 0.275 ...
 $ Time Body Acceleration Mean Y                                : num  -0.0233 -0.0132 -0.0261 -0.0326 -0.0278 ...
 $ Time Body Acceleration Mean Z                                : num  -0.0147 -0.1191 -0.1182 -0.1175 -0.1295 ...
 $ Time Body Acceleration Standard Deviation X                  : num  -0.938 -0.975 -0.994 -0.995 -0.994 ...
 $ Time Body Acceleration Standard Deviation Y                  : num  -0.92 -0.967 -0.97 -0.973 -0.967 ...
 $ Time Body Acceleration Standard Deviation Z                  : num  -0.668 -0.945 -0.963 -0.967 -0.978 ...
 $ Time Gravity Acceleration Mean X                             : num  0.936 0.927 0.93 0.929 0.927 ...
 $ Time Gravity Acceleration Mean Y                             : num  -0.283 -0.289 -0.288 -0.293 -0.303 ...
 $ Time Gravity Acceleration Mean Z                             : num  0.115 0.153 0.146 0.143 0.138 ...
 $ Time Gravity Acceleration Standard Deviation X               : num  -0.925 -0.989 -0.996 -0.993 -0.996 ...
 $ Time Gravity Acceleration Standard Deviation Y               : num  -0.937 -0.984 -0.988 -0.97 -0.971 ...
 $ Time Gravity Acceleration Standard Deviation Z               : num  -0.564 -0.965 -0.982 -0.992 -0.968 ...
 $ Time Body Acceleration Jerk Mean X                           : num  0.072 0.0702 0.0694 0.0749 0.0784 ...
 $ Time Body Acceleration Jerk Mean Y                           : num  0.04575 -0.01788 -0.00491 0.03227 0.02228 ...
 $ Time Body Acceleration Jerk Mean Z                           : num  -0.10604 -0.00172 -0.01367 0.01214 0.00275 ...
 $ Time Body Acceleration Jerk Standard Deviation X             : num  -0.907 -0.949 -0.991 -0.991 -0.992 ...
 $ Time Body Acceleration Jerk Standard Deviation Y             : num  -0.938 -0.973 -0.971 -0.973 -0.979 ...
 $ Time Body Acceleration Jerk Standard Deviation Z             : num  -0.936 -0.978 -0.973 -0.976 -0.987 ...
 $ Time Body Gyroscope Mean X                                   : num  0.11998 -0.00155 -0.04821 -0.05664 -0.05999 ...
 $ Time Body Gyroscope Mean Y                                   : num  -0.0918 -0.1873 -0.1663 -0.126 -0.0847 ...
 $ Time Body Gyroscope Mean Z                                   : num  0.1896 0.1807 0.1542 0.1183 0.0787 ...
 $ Time Body Gyroscope Standard Deviation X                     : num  -0.883 -0.926 -0.973 -0.968 -0.975 ...
 $ Time Body Gyroscope Standard Deviation Y                     : num  -0.816 -0.93 -0.979 -0.975 -0.978 ...
 $ Time Body Gyroscope Standard Deviation Z                     : num  -0.941 -0.968 -0.976 -0.963 -0.968 ...
 $ Time Body Gyroscope Jerk Mean X                              : num  -0.2049 -0.1387 -0.0978 -0.1022 -0.0918 ...
 $ Time Body Gyroscope Jerk Mean Y                              : num  -0.1745 -0.0258 -0.0342 -0.0447 -0.029 ...
 $ Time Body Gyroscope Jerk Mean Z                              : num  -0.0934 -0.0714 -0.06 -0.0534 -0.0612 ...
 $ Time Body Gyroscope Jerk Standard Deviation X                : num  -0.901 -0.962 -0.984 -0.984 -0.988 ...
 $ Time Body Gyroscope Jerk Standard Deviation Y                : num  -0.911 -0.956 -0.988 -0.99 -0.992 ...
 $ Time Body Gyroscope Jerk Standard Deviation Z                : num  -0.939 -0.981 -0.976 -0.981 -0.982 ...
 $ Time Body Acceleration Magnitude Mean                        : num  -0.867 -0.969 -0.976 -0.974 -0.976 ...
 $ Time Body Acceleration Magnitude Standard Deviation          : num  -0.705 -0.954 -0.979 -0.977 -0.977 ...
 $ Time Gravity Acceleration Magnitude Mean                     : num  -0.867 -0.969 -0.976 -0.974 -0.976 ...
 $ Time Gravity Acceleration Magnitude Standard Deviation       : num  -0.705 -0.954 -0.979 -0.977 -0.977 ...
 $ Time Body Acceleration Jerk Magnitude Mean                   : num  -0.93 -0.974 -0.982 -0.983 -0.987 ...
 $ Time Body Acceleration Jerk Magnitude Standard Deviation     : num  -0.896 -0.941 -0.971 -0.975 -0.989 ...
 $ Time Body Gyroscope Magnitude Mean                           : num  -0.796 -0.898 -0.939 -0.947 -0.957 ...
 $ Time Body Gyroscope Magnitude Standard Deviation             : num  -0.762 -0.911 -0.972 -0.97 -0.969 ...
 $ Time Body Gyroscope Jerk Magnitude Mean                      : num  -0.925 -0.973 -0.987 -0.989 -0.99 ...
 $ Time Body Gyroscope Jerk Magnitude Standard Deviation        : num  -0.894 -0.944 -0.984 -0.986 -0.99 ...
 $ Frequency Body Acceleration Mean X                           : num  -0.919 -0.961 -0.992 -0.993 -0.992 ...
 $ Frequency Body Acceleration Mean Y                           : num  -0.918 -0.964 -0.965 -0.968 -0.969 ...
 $ Frequency Body Acceleration Mean Z                           : num  -0.789 -0.957 -0.967 -0.967 -0.98 ...
 $ Frequency Body Acceleration Standard Deviation X             : num  -0.948 -0.984 -0.995 -0.996 -0.995 ...
 $ Frequency Body Acceleration Standard Deviation Y             : num  -0.925 -0.97 -0.974 -0.977 -0.967 ...
 $ Frequency Body Acceleration Standard Deviation Z             : num  -0.636 -0.942 -0.962 -0.969 -0.978 ...
 $ Frequency Body Acceleration Mean q...X                       : num  0.0111 0.3521 0.1804 0.0627 -0.0189 ...
 $ Frequency Body Acceleration Mean q...Y                       : num  0.12125 0.17455 0.13346 0.26172 -0.00998 ...
 $ Frequency Body Acceleration Mean q...Z                       : num  -0.5229 -0.3207 0.1827 0.1518 0.0952 ...
 $ Frequency Body Acceleration Jerk Mean X                      : num  -0.9 -0.944 -0.991 -0.991 -0.991 ...
 $ Frequency Body Acceleration Jerk Mean Y                      : num  -0.937 -0.969 -0.973 -0.972 -0.98 ...
 $ Frequency Body Acceleration Jerk Mean Z                      : num  -0.924 -0.973 -0.972 -0.97 -0.983 ...
 $ Frequency Body Acceleration Jerk Standard Deviation X        : num  -0.924 -0.962 -0.992 -0.992 -0.994 ...
 $ Frequency Body Acceleration Jerk Standard Deviation Y        : num  -0.943 -0.98 -0.971 -0.975 -0.979 ...
 $ Frequency Body Acceleration Jerk Standard Deviation Z        : num  -0.948 -0.981 -0.972 -0.981 -0.989 ...
 $ Frequency Body Acceleration Jerk Mean q...X                  : num  0.451 0.473 0.271 0.277 0.18 ...
 $ Frequency Body Acceleration Jerk Mean q...Y                  : num  0.1372 0.1672 -0.2722 -0.0383 -0.1392 ...
 $ Frequency Body Acceleration Jerk Mean q...Z                  : num  -0.1803 -0.2431 -0.0825 0.0218 0.1009 ...
 $ Frequency Body Gyroscope Mean X                              : num  -0.824 -0.923 -0.973 -0.972 -0.976 ...
 $ Frequency Body Gyroscope Mean Y                              : num  -0.808 -0.926 -0.981 -0.981 -0.98 ...
 $ Frequency Body Gyroscope Mean Z                              : num  -0.918 -0.968 -0.972 -0.967 -0.969 ...
 $ Frequency Body Gyroscope Standard Deviation X                : num  -0.903 -0.927 -0.973 -0.967 -0.974 ...
 $ Frequency Body Gyroscope Standard Deviation Y                : num  -0.823 -0.932 -0.977 -0.972 -0.977 ...
 $ Frequency Body Gyroscope Standard Deviation Z                : num  -0.956 -0.97 -0.979 -0.965 -0.97 ...
 $ Frequency Body Gyroscope Mean q...X                          : num  0.184 0.0181 -0.4791 -0.497 -0.4275 ...
 $ Frequency Body Gyroscope Mean q...Y                          : num  -0.0593 -0.2273 -0.2101 -0.4999 -0.2781 ...
 $ Frequency Body Gyroscope Mean q...Z                          : num  0.4381 -0.1517 0.0493 -0.2589 -0.2913 ...
 $ Frequency Body Acceleration Magnitude Mean                   : num  -0.791 -0.954 -0.976 -0.973 -0.978 ...
 $ Frequency Body Acceleration Magnitude Standard Deviation     : num  -0.711 -0.96 -0.984 -0.982 -0.979 ...
 $ Frequency Body Acceleration Magnitude Mean q..               : num  -0.4835 0.2035 0.3425 0.3312 0.0711 ...
 $ Frequency Body Acceleration Jerk Magnitude Mean              : num  -0.895 -0.945 -0.971 -0.972 -0.987 ...
 $ Frequency Body Acceleration Jerk Magnitude Standard Deviation: num  -0.896 -0.934 -0.97 -0.978 -0.99 ...
 $ Frequency Body Acceleration Jerk Magnitude Mean q..          : num  -0.0354 -0.4912 0.1407 0.1486 0.4222 ...
 $ Frequency Body Gyroscope Magnitude Mean                      : num  -0.771 -0.924 -0.975 -0.976 -0.977 ...
 $ Frequency Body Gyroscope Magnitude Standard Deviation        : num  -0.797 -0.917 -0.974 -0.971 -0.97 ...
 $ Frequency Body Gyroscope Magnitude Mean q..                  : num  -0.0474 -0.0315 -0.1688 -0.2856 -0.3491 ...
 $ Frequency Body Gyroscope Jerk Magnitude Mean                 : num  -0.89 -0.952 -0.986 -0.986 -0.99 ...
 $ Frequency Body Gyroscope Jerk Magnitude Standard Deviation   : num  -0.907 -0.938 -0.983 -0.986 -0.991 ...
 $ Frequency Body Gyroscope Jerk Magnitude Mean q..             : num  0.0716 -0.4012 0.0629 0.1167 -0.1217 ...
```
#### Final data set with means by subject and activity
```{r, eval=F}
str(add.tidy.data)

grouped_df [180 x 81] (S3: grouped_df/tbl_df/tbl/data.frame)
 $ subject                                                      : int [1:180] 1 1 1 1 1 1 2 2 2 2 ...
 $ Activity                                                     : chr [1:180] "LAYING" "SITTING" "STANDING" "WALKING" ...
 $ Time Body Acceleration Mean X                                : num [1:180] 0.222 0.261 0.279 0.277 0.289 ...
 $ Time Body Acceleration Mean Y                                : num [1:180] -0.04051 -0.00131 -0.01614 -0.01738 -0.00992 ...
 $ Time Body Acceleration Mean Z                                : num [1:180] -0.113 -0.105 -0.111 -0.111 -0.108 ...
 $ Time Body Acceleration Standard Deviation X                  : num [1:180] -0.928 -0.977 -0.996 -0.284 0.03 ...
 $ Time Body Acceleration Standard Deviation Y                  : num [1:180] -0.8368 -0.9226 -0.9732 0.1145 -0.0319 ...
 $ Time Body Acceleration Standard Deviation Z                  : num [1:180] -0.826 -0.94 -0.98 -0.26 -0.23 ...
 $ Time Gravity Acceleration Mean X                             : num [1:180] -0.249 0.832 0.943 0.935 0.932 ...
 $ Time Gravity Acceleration Mean Y                             : num [1:180] 0.706 0.204 -0.273 -0.282 -0.267 ...
 $ Time Gravity Acceleration Mean Z                             : num [1:180] 0.4458 0.332 0.0135 -0.0681 -0.0621 ...
 $ Time Gravity Acceleration Standard Deviation X               : num [1:180] -0.897 -0.968 -0.994 -0.977 -0.951 ...
 $ Time Gravity Acceleration Standard Deviation Y               : num [1:180] -0.908 -0.936 -0.981 -0.971 -0.937 ...
 $ Time Gravity Acceleration Standard Deviation Z               : num [1:180] -0.852 -0.949 -0.976 -0.948 -0.896 ...
 $ Time Body Acceleration Jerk Mean X                           : num [1:180] 0.0811 0.0775 0.0754 0.074 0.0542 ...
 $ Time Body Acceleration Jerk Mean Y                           : num [1:180] 0.003838 -0.000619 0.007976 0.028272 0.02965 ...
 $ Time Body Acceleration Jerk Mean Z                           : num [1:180] 0.01083 -0.00337 -0.00369 -0.00417 -0.01097 ...
 $ Time Body Acceleration Jerk Standard Deviation X             : num [1:180] -0.9585 -0.9864 -0.9946 -0.1136 -0.0123 ...
 $ Time Body Acceleration Jerk Standard Deviation Y             : num [1:180] -0.924 -0.981 -0.986 0.067 -0.102 ...
 $ Time Body Acceleration Jerk Standard Deviation Z             : num [1:180] -0.955 -0.988 -0.992 -0.503 -0.346 ...
 $ Time Body Gyroscope Mean X                                   : num [1:180] -0.0166 -0.0454 -0.024 -0.0418 -0.0351 ...
 $ Time Body Gyroscope Mean Y                                   : num [1:180] -0.0645 -0.0919 -0.0594 -0.0695 -0.0909 ...
 $ Time Body Gyroscope Mean Z                                   : num [1:180] 0.1487 0.0629 0.0748 0.0849 0.0901 ...
 $ Time Body Gyroscope Standard Deviation X                     : num [1:180] -0.874 -0.977 -0.987 -0.474 -0.458 ...
 $ Time Body Gyroscope Standard Deviation Y                     : num [1:180] -0.9511 -0.9665 -0.9877 -0.0546 -0.1263 ...
 $ Time Body Gyroscope Standard Deviation Z                     : num [1:180] -0.908 -0.941 -0.981 -0.344 -0.125 ...
 $ Time Body Gyroscope Jerk Mean X                              : num [1:180] -0.1073 -0.0937 -0.0996 -0.09 -0.074 ...
 $ Time Body Gyroscope Jerk Mean Y                              : num [1:180] -0.0415 -0.0402 -0.0441 -0.0398 -0.044 ...
 $ Time Body Gyroscope Jerk Mean Z                              : num [1:180] -0.0741 -0.0467 -0.049 -0.0461 -0.027 ...
 $ Time Body Gyroscope Jerk Standard Deviation X                : num [1:180] -0.919 -0.992 -0.993 -0.207 -0.487 ...
 $ Time Body Gyroscope Jerk Standard Deviation Y                : num [1:180] -0.968 -0.99 -0.995 -0.304 -0.239 ...
 $ Time Body Gyroscope Jerk Standard Deviation Z                : num [1:180] -0.958 -0.988 -0.992 -0.404 -0.269 ...
 $ Time Body Acceleration Magnitude Mean                        : num [1:180] -0.8419 -0.9485 -0.9843 -0.137 0.0272 ...
 $ Time Body Acceleration Magnitude Standard Deviation          : num [1:180] -0.7951 -0.9271 -0.9819 -0.2197 0.0199 ...
 $ Time Gravity Acceleration Magnitude Mean                     : num [1:180] -0.8419 -0.9485 -0.9843 -0.137 0.0272 ...
 $ Time Gravity Acceleration Magnitude Standard Deviation       : num [1:180] -0.7951 -0.9271 -0.9819 -0.2197 0.0199 ...
 $ Time Body Acceleration Jerk Magnitude Mean                   : num [1:180] -0.9544 -0.9874 -0.9924 -0.1414 -0.0894 ...
 $ Time Body Acceleration Jerk Magnitude Standard Deviation     : num [1:180] -0.9282 -0.9841 -0.9931 -0.0745 -0.0258 ...
 $ Time Body Gyroscope Magnitude Mean                           : num [1:180] -0.8748 -0.9309 -0.9765 -0.161 -0.0757 ...
 $ Time Body Gyroscope Magnitude Standard Deviation             : num [1:180] -0.819 -0.935 -0.979 -0.187 -0.226 ...
 $ Time Body Gyroscope Jerk Magnitude Mean                      : num [1:180] -0.963 -0.992 -0.995 -0.299 -0.295 ...
 $ Time Body Gyroscope Jerk Magnitude Standard Deviation        : num [1:180] -0.936 -0.988 -0.995 -0.325 -0.307 ...
 $ Frequency Body Acceleration Mean X                           : num [1:180] -0.9391 -0.9796 -0.9952 -0.2028 0.0382 ...
 $ Frequency Body Acceleration Mean Y                           : num [1:180] -0.86707 -0.94408 -0.97707 0.08971 0.00155 ...
 $ Frequency Body Acceleration Mean Z                           : num [1:180] -0.883 -0.959 -0.985 -0.332 -0.226 ...
 $ Frequency Body Acceleration Standard Deviation X             : num [1:180] -0.9244 -0.9764 -0.996 -0.3191 0.0243 ...
 $ Frequency Body Acceleration Standard Deviation Y             : num [1:180] -0.834 -0.917 -0.972 0.056 -0.113 ...
 $ Frequency Body Acceleration Standard Deviation Z             : num [1:180] -0.813 -0.934 -0.978 -0.28 -0.298 ...
 $ Frequency Body Acceleration Mean q...X                       : num [1:180] -0.1588 -0.0495 0.0865 -0.2075 -0.3074 ...
 $ Frequency Body Acceleration Mean q...Y                       : num [1:180] 0.0975 0.0759 0.1175 0.1131 0.0632 ...
 $ Frequency Body Acceleration Mean q...Z                       : num [1:180] 0.0894 0.2388 0.2449 0.0497 0.2943 ...
 $ Frequency Body Acceleration Jerk Mean X                      : num [1:180] -0.9571 -0.9866 -0.9946 -0.1705 -0.0277 ...
 $ Frequency Body Acceleration Jerk Mean Y                      : num [1:180] -0.9225 -0.9816 -0.9854 -0.0352 -0.1287 ...
 $ Frequency Body Acceleration Jerk Mean Z                      : num [1:180] -0.948 -0.986 -0.991 -0.469 -0.288 ...
 $ Frequency Body Acceleration Jerk Standard Deviation X        : num [1:180] -0.9642 -0.9875 -0.9951 -0.1336 -0.0863 ...
 $ Frequency Body Acceleration Jerk Standard Deviation Y        : num [1:180] -0.932 -0.983 -0.987 0.107 -0.135 ...
 $ Frequency Body Acceleration Jerk Standard Deviation Z        : num [1:180] -0.961 -0.988 -0.992 -0.535 -0.402 ...
 $ Frequency Body Acceleration Jerk Mean q...X                  : num [1:180] 0.132 0.257 0.314 -0.209 -0.253 ...
 $ Frequency Body Acceleration Jerk Mean q...Y                  : num [1:180] 0.0245 0.0475 0.0392 -0.3862 -0.3376 ...
 $ Frequency Body Acceleration Jerk Mean q...Z                  : num [1:180] 0.02439 0.09239 0.13858 -0.18553 0.00937 ...
 $ Frequency Body Gyroscope Mean X                              : num [1:180] -0.85 -0.976 -0.986 -0.339 -0.352 ...
 $ Frequency Body Gyroscope Mean Y                              : num [1:180] -0.9522 -0.9758 -0.989 -0.1031 -0.0557 ...
 $ Frequency Body Gyroscope Mean Z                              : num [1:180] -0.9093 -0.9513 -0.9808 -0.2559 -0.0319 ...
 $ Frequency Body Gyroscope Standard Deviation X                : num [1:180] -0.882 -0.978 -0.987 -0.517 -0.495 ...
 $ Frequency Body Gyroscope Standard Deviation Y                : num [1:180] -0.9512 -0.9623 -0.9871 -0.0335 -0.1814 ...
 $ Frequency Body Gyroscope Standard Deviation Z                : num [1:180] -0.917 -0.944 -0.982 -0.437 -0.238 ...
 $ Frequency Body Gyroscope Mean q...X                          : num [1:180] -0.00355 0.18915 -0.12029 0.01478 -0.10045 ...
 $ Frequency Body Gyroscope Mean q...Y                          : num [1:180] -0.0915 0.0631 -0.0447 -0.0658 0.0826 ...
 $ Frequency Body Gyroscope Mean q...Z                          : num [1:180] 0.010458 -0.029784 0.100608 0.000773 -0.075676 ...
 $ Frequency Body Acceleration Magnitude Mean                   : num [1:180] -0.8618 -0.9478 -0.9854 -0.1286 0.0966 ...
 $ Frequency Body Acceleration Magnitude Standard Deviation     : num [1:180] -0.798 -0.928 -0.982 -0.398 -0.187 ...
 $ Frequency Body Acceleration Magnitude Mean q..               : num [1:180] 0.0864 0.2367 0.2846 0.1906 0.1192 ...
 $ Frequency Body Acceleration Jerk Magnitude Mean              : num [1:180] -0.9333 -0.9853 -0.9925 -0.0571 0.0262 ...
 $ Frequency Body Acceleration Jerk Magnitude Standard Deviation: num [1:180] -0.922 -0.982 -0.993 -0.103 -0.104 ...
 $ Frequency Body Acceleration Jerk Magnitude Mean q..          : num [1:180] 0.2664 0.3519 0.4222 0.0938 0.0765 ...
 $ Frequency Body Gyroscope Magnitude Mean                      : num [1:180] -0.862 -0.958 -0.985 -0.199 -0.186 ...
 $ Frequency Body Gyroscope Magnitude Standard Deviation        : num [1:180] -0.824 -0.932 -0.978 -0.321 -0.398 ...
 $ Frequency Body Gyroscope Magnitude Mean q..                  : num [1:180] -0.139775 -0.000262 -0.028606 0.268844 0.349614 ...
 $ Frequency Body Gyroscope Jerk Magnitude Mean                 : num [1:180] -0.942 -0.99 -0.995 -0.319 -0.282 ...
 $ Frequency Body Gyroscope Jerk Magnitude Standard Deviation   : num [1:180] -0.933 -0.987 -0.995 -0.382 -0.392 ...
 $ Frequency Body Gyroscope Jerk Magnitude Mean q..             : num [1:180] 0.176 0.185 0.334 0.191 0.19 ...
 - attr(*, "groups")= tibble [30 x 2] (S3: tbl_df/tbl/data.frame)
  ..$ subject: int [1:30] 1 2 3 4 5 6 7 8 9 10 ...
  ..$ .rows  : list<int> [1:30] 
  .. ..$ : int [1:6] 1 2 3 4 5 6
  .. ..$ : int [1:6] 7 8 9 10 11 12
  .. ..$ : int [1:6] 13 14 15 16 17 18
  .. ..$ : int [1:6] 19 20 21 22 23 24
  .. ..$ : int [1:6] 25 26 27 28 29 30
  .. ..$ : int [1:6] 31 32 33 34 35 36
  .. ..$ : int [1:6] 37 38 39 40 41 42
  .. ..$ : int [1:6] 43 44 45 46 47 48
  .. ..$ : int [1:6] 49 50 51 52 53 54
  .. ..$ : int [1:6] 55 56 57 58 59 60
  .. ..$ : int [1:6] 61 62 63 64 65 66
  .. ..$ : int [1:6] 67 68 69 70 71 72
  .. ..$ : int [1:6] 73 74 75 76 77 78
  .. ..$ : int [1:6] 79 80 81 82 83 84
  .. ..$ : int [1:6] 85 86 87 88 89 90
  .. ..$ : int [1:6] 91 92 93 94 95 96
  .. ..$ : int [1:6] 97 98 99 100 101 102
  .. ..$ : int [1:6] 103 104 105 106 107 108
  .. ..$ : int [1:6] 109 110 111 112 113 114
  .. ..$ : int [1:6] 115 116 117 118 119 120
  .. ..$ : int [1:6] 121 122 123 124 125 126
  .. ..$ : int [1:6] 127 128 129 130 131 132
  .. ..$ : int [1:6] 133 134 135 136 137 138
  .. ..$ : int [1:6] 139 140 141 142 143 144
  .. ..$ : int [1:6] 145 146 147 148 149 150
  .. ..$ : int [1:6] 151 152 153 154 155 156
  .. ..$ : int [1:6] 157 158 159 160 161 162
  .. ..$ : int [1:6] 163 164 165 166 167 168
  .. ..$ : int [1:6] 169 170 171 172 173 174
  .. ..$ : int [1:6] 175 176 177 178 179 180
  .. ..@ ptype: int(0) 
  ..- attr(*, ".drop")= logi TRUE

```

